\stdpopsim: a community-supported toolkit for population genetic simulation

### 2019-12-05 popSimManu.tex
Added table to manuscript.
Incidental changes are automatic empty space deletes.
Fixed bibliography filename.
Reworked abstract.

\abstract{The explosion in population genomic data demands ever increasingly complex modes of analysis.
More and more these analyses depend on sophisticated, often computationally expensive simulation. 
To date, computational genetics researchers have been often forced to re-implement such simulations
independently, leading to both wasted time in the duplication of effort and reductions in reproducibility.
Population genetics, as a field, specifically lacks rigorous standard benchmarks by which new tools for inference might 
be measured. Here we describe a new resource, the PopSim library, that attempts to rectify this situation. 
PopSim is a community-driven, open source project, aimed at revolutionizing the ease and reproducibility
of population genetic simulation for a catalog of published demographic models from both humans and non-model organisms. 
PopSim assures correctness in our implementations through a mature quality control pipeline that is
community-based. Here we describe the PopSim resource as a step towards inviting an even broader
community of developers to participate and demonstrate some rather simple examples of how one
might use PopSim for comparison of methods of demographic inference.}

\date{\today}

@@

@@

\bibliographystyle{plainnat}
\bibliography{PopSim.bib}

>>>>

% JK: didn't bother with the \texttt stuff for stdpopsim in the abstract as it's nearly
% always dropped in production anyway.

\abstract{The explosion in population genomic data demands ever more complex
modes of analysis, and increasingly these analyses depend on sophisticated simulations.
Recent advances in population genetic simulation have made it possible to
simulate large and complex models, but describing such models for a particular
simulation engine remains a difficult and error-prone task.
Computational genetics researchers currently re-implement simulation models
independently, leading to duplication of effort and reductions in reproducibility.
Population genetics, as a field, also lacks rigorous standard benchmarks by which new tools for inference might
be measured. Here we describe a new resource, stdpopsim, that attempts to rectify this situation.
Stdpopsim is a community-driven, open source project, which provides a standard
catalog of published simulation models from a wide range of organisms,
and supports multiple simulation engine backends.
% PopSim assures correctness in our implementations through a mature quality control pipeline that is community-based.
Here we describe the stdpopsim resource to encourange an even broader
community of developers to participate and to demonstrate some examples of how
it can be used to systematically compare demographic inference methods.}
\date{\today}

@@

\begin{table}
\begin{footnotesize}
\input{model_table.tex}
\end{footnotesize}
\caption{\label{tab:catalog}
Details of the initial set of population models across four species.
\textbf{NOTES: Column names are ID, name (or description maybe?),
reference, CPU time, RAM}
}
\end{table}

@@

\bibliographystyle{plainnat}
\bibliography{popSim.bib}
